---
title: "Statistical_Method_Assignment"
author: "Dimitra Muni (LiU ID: dimmu472)"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 4.84 Gamma Distribution

```{r}
hist(rgamma(10000,shape = 4,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",4," ",beta,"=",1)))
hist(rgamma(10000,shape = 40,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",40," ",beta,"=",1)))
hist(rgamma(10000,shape = 80,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",80," ",beta,"=",1)))
```

**(a)** What do you observe about the shapes of these three density functions? Which are less skewed and more symmetric? 

Gamma distribution for constant beta value, as the alpha increases becomes less skewed,For alpha 40 and 80 it get more symmetric as compared to alpha=1.

**(b)** What differences do you observe about the location of the centers of these density functions?

Location of centers correspond to shape(alpha) parameter in the density function, its centered around alpha and its porportional to it.

**(c)** Give an explanation for what you observed in part (b)

As the alpha increases location centers increase.



# 4.117 Beta Distribution

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =9, shape2 =7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =10, shape2 =7),type ="l", col=3)
lines(dbeta(p,shape1 =12, shape2 =7),type ="l", col=4)
legend(0.1,2.3, c("Beta(9,7)","Beta(10,7)", "Beta(12,7)"),lty=c(1,1,1),col=c(2,3,4))
```
**(a)** Are these densities symmetric? Skewed left? Skewed right?

These densities are skewed right, they are not symmetric.

**(b)** What do you observe as the value of α gets closer to 12?

As α gets closer to 12,the values are less spread out (more concentrated and symmetric).

**(c)** Graph some more beta densities with α > 1,β> 1, and α>β. What do you conjecture about the shape of beta densities with α>β and both α > 1 and β > 1? 

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =10, shape2 =7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =20, shape2 =7),type ="l", col=3)
lines(dbeta(p,shape1 =7, shape2 =10),type ="l", col=4)
lines(dbeta(p,shape1 =7, shape2 =20),type ="l", col=6)
legend(0.1,2.3, c("Beta(10,7)","Beta(20,7)", "Beta(7,10)","Beta(7,20)"),lty=c(1,1,1,1),col=c(2,3,4,6))
```

For α > 1,β> 1 it can be observed that, for constant β value increasing α value results in distribution skewed towards right
While for constant α value, increasing β has distribution skewed towards left.

Now, for α>β,
when α > 1,β> 1, It can be observed that when α is increasing its skewed towards right, and the dispersion is less.It becomes more focused.

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =0.9, shape2 =0.7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =0.9, shape2 =0.07),type ="l", col=3)
legend(0.1,2.3, c("Beta(0.9,0.7)","Beta(0.9,0.07)"),lty=c(1,1),col=c(2,3))
```

when, 0< β< α < 1, The distribution has exponential behavior.When the difference between them is large, it grows even faster.


# 4.118  Beta Density Functions

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =0.3, shape2 =4), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =0.3, shape2 =7),type ="l", col=3)
lines(dbeta(p,shape1 =0.3, shape2 =12),type ="l", col=4)
legend(60,10, c("Beta(0.3,4)","Beta(0.3,7)", "Beta(0.3,12)"),lty=c(1,1,1),col=c(2,3,4))
```

**(a)** Are these densities symmetric? Skewed left? Skewed right?

Here densities are skewed right.

**(b)** What do you observe as the value of β gets closer to 12?

As value of β gets closer to 12 the curve is get more sharper with less spread.And for higher value of β, it acts as signum function

**(c)** Which of these beta distributions gives the highest probability of observing a value larger than 0.2? 
```{r}
pbeta(0.2, shape1=0.3, shape2=4,lower.tail = FALSE)
pbeta(0.2, shape1=0.3, shape2=7,lower.tail = FALSE)
pbeta(0.2, shape1=0.3, shape2=12,lower.tail = FALSE)
```
For alpha=0.3 and beta=4 distribution has higest probability of observing value larger than 0.2

**(d)** Graph some more beta densities with α < 1 and β > 1. 

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =0.3, shape2 =4), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =0.03, shape2 =4),type ="l", col=3)
lines(dbeta(p,shape1 =0.003, shape2 =4),type ="l", col=4)
legend(60,10, c("Beta(0.3,4)","Beta(0.3,7)", "Beta(0.3,12)"),lty=c(1,1,1),col=c(2,3,4))
```
What do you conjecture about the shape of beta densities with α < 1 and β > 1?

All of these have similar shape but by reducing α by factor of 10, made the curve sharper.





# 10.19  Voltage Hypothesis Testing

The output voltage for an electric circuit is specified to be 130.
A sample of 40 independent readings on the voltage for this circuit gave a sample mean 128.6 and standard deviation 2.1.
Test the hypothesis that the average output voltage is 130 against the alternative that it is less than 130. Use a test with level .05.

Ho:mean=130

Ha:mean<130

```{r}

n=40
m=128.6
sd=2.1
mean=130
Z=(m-mean)/(sd/sqrt(n))
Z
```
For α = .05, we have -z(α)=-1.645. As |Z|>z. we reject Ho.

# 10.21 Shear strength Hypothesis Testing

Shear strength measurements derived from unconfined compression tests for two types of soils gave the results shown in the following table (measurements in tons per square foot). Do the soils appear to differ with respect to average shear strength, at the 1% significance level?

Ho:Both have the same shear strength

Ha:Both differ in the shear strength

Here as its two tailed test,with α = .01
```{r}
n1 = 30
n2 = 35 
y1 = 1.65 
y2 = 1.43 
s1 = 0.26 
s2 = 0.22

Z=(y1-y2)/sqrt((s1^2)/n1 + (s2^2)/n2)
Z
```
Here we obtain Z=3.65. With 
α = .01 we have z(α/2) =z(.005)=2.575
As Z>z, we can reject the hypothesis that they have the same shear strength.


# 11.31 Nickel Concentration

Using a chemical procedure called differential pulse polarography, a chemist measured the peak current generated (in microamperes, μA) when solutions containing different amounts of nickel (measured in parts per billion, ppb) are added to different portions of the same buffer.Is there sufficient evidence to indicate that peak current increases as nickel concentrations increase? Use α = .05.

Ho: peak current doesn't increase (i.e. constant or decreases) (y=constant) with increase in nickel concentration
Ha: peak current increases with increase in nickel concentration

```{r}

x<-c(19.1,38.2,57.3,76.2,95,114,131,150,170)
y<-c(0.095,0.174,0.256,0.348,0.429,0.5,0.58,0.651,0.722)
summary(lm(y~x))
```
Here p-value is (2.372e-11)/2 (two-tailed) which is quite small we can reject the Ho here.

# 11.69 Lexus Automobile modeling

**(a)** fit the model Y = β0 + β1*x + ε.

```{r}
x<-c(-7,-5,-3,-1,1,3,5,7)
y<-c(18.5,22.6,27.2,31.2,33,44.9,49.4,35)


lm(y~x)
```
y= 32.725+(1.812*x)

**b)** fit the model Y = β0 + β1*x + β2*x^2 + ε.

```{r}
x<-c(-7,-5,-3,-1,1,3,5,7)
y<-c(18.5,22.6,27.2,31.2,33,44.9,49.4,35)
lm(y~x+I(x^2))
```
y= 35.5625+1.8119*x-0.1351*x^2