---
title: "Statistical_Method_Assignment"
author: "Dimitra Muni (LiU ID: dimmu472)"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 4.84 Gamma Distribution

```{r}
hist(rgamma(10000,shape = 4,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",4," ",beta,"=",1)))
hist(rgamma(10000,shape = 40,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",40," ",beta,"=",1)))
hist(rgamma(10000,shape = 80,scale = 1),breaks = 100,main = expression(paste("Gamma Distribution ",alpha,"=",80," ",beta,"=",1)))
```

**a** What do you observe about the shapes of these three density functions? Which are less skewed and more symmetric? 
Gamma distribution for constant beta value, as the alpha increases becomes less skewed,For alpha 40 and 80 it get more symmetric as compared to alpha=1.

**b** What differences do you observe about the location of the centers of these density functions?
Location of centers correspond to shape(alpha) parameter in the density function, its centered around alpha.

**c** Give an explanation for what you observed in part (b)


# 4.117 Beta Distribution

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =9, shape2 =7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =10, shape2 =7),type ="l", col=3)
lines(dbeta(p,shape1 =12, shape2 =7),type ="l", col=4)
legend(0.1,2.3, c("Beta(9,7)","Beta(10,7)", "Beta(12,7)"),lty=c(1,1,1),col=c(2,3,4))
```
**a** Are these densities symmetric? Skewed left? Skewed right?
These densities are skewed right, they are not symmetric.

**b** What do you observe as the value of α gets closer to 12?
As α gets closer to 12,the values are less spread out (more concentrated).

**c** Graph some more beta densities with α > 1,β> 1, and α>β. What do you conjecture about the shape of beta densities with α>β and both α > 1 and β > 1? 

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =10, shape2 =7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =20, shape2 =7),type ="l", col=3)
lines(dbeta(p,shape1 =7, shape2 =10),type ="l", col=4)
lines(dbeta(p,shape1 =7, shape2 =20),type ="l", col=6)
legend(0.1,2.3, c("Beta(10,7)","Beta(20,7)", "Beta(7,10)","Beta(7,20)"),lty=c(1,1,1,1),col=c(2,3,4,6))
```

For α > 1,β> 1 it can be observed that, for constant β value increasing α value results in distribution skewed towards right
While for constant α value, increasing β has distribution skewed towards left.

Now, for α>β

when α > 1,β> 1, It can be observed that when α is increasing its skewed towards right, and the dispersion is less.It becomes more focused.

```{r}
p=seq(0,1,length.out = 100)
plot(dbeta(p,shape1 =0.9, shape2 =0.7), ylab="density",type ="l", col=2)
lines(dbeta(p,shape1 =0.9, shape2 =0.07),type ="l", col=3)
legend(0.1,2.3, c("Beta(0.9,0.7)","Beta(0.9,0.07)"),lty=c(1,1),col=c(2,3))
```

when, 0< β< α < 1, The distribution has exponential behavior.When the difference between them is large, it grows even faster.


# 4.118
#Applet Exercise Use the applet Comparison of Beta Density Functions to compare beta density functions
# with (α = .3, β = 4), (α = .3, β = 7), and (α = .3, β = 12). a Are these densities symmetric? Skewed left? Skewed right?
# b What do you observe as the value of β gets closer to 12?
#   c Which of these beta distributions gives the highest probability of observing a value larger than 0.2? d Graph some more beta densities with α < 1 and β > 1. 
# What do you conjecture about the shape of beta densities with α < 1 and β > 1?


